Fast running systems requires many transistors, which makes the manufacturing process very hard.
Many Chips have millions or even billions of transistors which affects the circuit timing, power consumption, chip reliability and manufacturability that complicate all the design rules.
One of the most important challenge is routing to connect the transistors, without causing any problem on the chip.
Routing problem, in \emph{VLSI}, is considered an \emph{NP-hard} problem, so it is divided into two design phases, \emph{global routing} where the grid is constructed with its nodes and edges,
and \emph{detailed phase} (our target) to find shortest paths to connect the required pins in the grid together.
Many algorithms can be used to solve routing problem, as it can be formulated as grid search problem, where speedup and optimality are a trade-off.
We try \emph{Lee's}, \emph{Mikami-Tabuchi}, \emph{Steiner tree} and \emph{A* search} algorithms, where our main approach was A* search.
We compare the different algorithms based on their execution time and length of metal.



We discussed the Detailed Routing problem, and shows that it can be formulated as gird search problem.
A* algorithm with euclidean distance as cost function was our main approach in the problem solution.
We tried different gird search techniques and compared their results with our main approach with respect to performance and time, and found that
A* achieves the better performance in some cases and same performance in the others in acceptable time compared to other algorithms.