\documentclass[conference,11pt]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage[verbose,expansion=alltext,stretch=50]{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{xcolor}
\usepackage{float}
\usepackage{subcaption}
\usepackage[labelformat=parens,labelsep=quad,skip=3pt]{caption}

\newcommand{\link}[1]{{\color{blue}\href{#1}{#1}}}
\title{Exploring A* Search For Single and Multi Layer Routing}

\author{
    Team \#1\\
    \IEEEauthorblockN{
        Mohamed Shawky \small\texttt{SEC:2, BN:16}\IEEEauthorrefmark{1},
        Remonda Talaat \small\texttt{SEC:1, BN:20}\IEEEauthorrefmark{2},\\ 
        Mahmoud Othman Adas \small\texttt{SEC:2, BN:21}\IEEEauthorrefmark{3} and
        Evram Youssef \small\texttt{SEC:1, BN:9}\IEEEauthorrefmark{4}}
    \IEEEauthorblockA{
        \\Department of Computer Engineering,
        Cairo University\\
        Email: 
        \IEEEauthorrefmark{1}mohamed.sabae99@eng-st.cu.edu.eg,
        \IEEEauthorrefmark{2}Remonda.Bastawres99@eng-st.cu.edu.eg,\\
        \IEEEauthorrefmark{3}mahmoud.ibrahim97@eng-st.cu.edu.eg,
        \IEEEauthorrefmark{4}evram.narouz00@eng-st.cu.edu.eg
    }
}

\begin{document}
\maketitle

\begin{abstract}
The recent advances in supercomputers and massive data centres increase the demand for fast processing on various types of data. Consequently, high performance chips become one of the critical factors in any computational system. Modern chips can contain million or even billions of transistors to achieve high performance and demanded functionalities. This makes the process of their design, implementation and integration very tedious. One of the key challenges in modern chip manufacture is routing. Routing is the process of wiring different source transistors to their fan-outs. This process can be very complicated in huge chips and requires the usage of specialized software, which is known as automatic routing. Several research projects have worked on this problem and various techniques are proposed. These techniques are mainly a compromise between the execution time and the solution optimality. In this work, we propose the usage of A* search algorithm, with a simple modified cost function, to solve the routing problem in a grid search formulation. The proposed solution can achieve the same or even better results than the considered baselines, while maintaining a reasonable execution time.
\end{abstract}

\begin{IEEEkeywords}
vlsi, routing, grid search, a* search, maze, steiner tree, mikami-tabuchi
\end{IEEEkeywords}

\section{Introduction}
\input{core/introduction}

\section{Terminology}
\input{core/terminology}
\label{terminologySection}

\section{Related Work}
\input{core/related_work}

\section{Methodology}
\input{core/methodology}

\section{Experimental Results}
\input{core/exp_results}

\section{Conclusion}
\input{core/conclusion}

\medskip

\bibliographystyle{unsrt}
\bibliography{paper}
    
\end{document}
